IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-16 paper/real.tex
Add todo for Deian in real and rephrase a bit the intro to the section

\section{Real World Languages}
\label{sec:real}

In the introduction, we stated that the original motivation behind
this work was to formally specify a
coarse-grained information flow control language for JavaScript.
%
Indeed, our formalism serves as the theoretical foundation for two
IFC systems for JavaScript, built on top of Node.js as well as
the web browser engine Gecko.

In this section, we describe these two implementations.  Furthermore,
we consider how our formalism could be applied to the C programming
language and connect it to a previous IFC system for Haskell.
%
The goal of this section is to show the flexibility of the embedding in settings with
vastly different properties and discuss the
semantic gap that must be overcome to apply our formalism
to other systems.
%
%% Two of the systems we describe have been implemented: the Haskell
%% system~\cite{lio} and the COWL~\cite{swapi} system; we leave the
%% implementation of the IFC system for C to future work.

>>>>

\section{Real World Languages}
\label{sec:real}
\Red{ALE: Here, Deian needs to fit the core part of COWL, i.e., with no external
  effects. It will be nice to have the COWL API and map it to IFC-Inside}

In the introduction, we stated that the original motivation behind
this work was to formally specify a
coarse-grained information flow control language for JavaScript.
%
Indeed, we show how our formalism serves as the theoretical foundation for the
core part of COWL~\cite{swapi}, a recent client-side coarse-grained IFC system
for Firefox.
%the web browser engine Gecko.

%IFC systems for JavaScript, built on top of Node.js as well as

%% Furthermore,
%% we consider how our formalism could be applied to the C programming
%% language and connect it to a previous IFC system for Haskell.
%% %
%% The goal of this section is to show the flexibility of the embedding in settings with
%% vastly different properties and discuss the
%% semantic gap that must be overcome to apply our formalism
%% to other systems.
%
%% Two of the systems we describe have been implemented: the Haskell
%% system~\cite{lio} and the COWL~\cite{swapi} system; we leave the
%% implementation of the IFC system for C to future work.
